Combining information from photometric and spectroscopic data:\\ Probabilistic spectrophotometric inference

### 2015-07-02 tex/ms.tex
more plot prettifying, comment out nebular lines from model description, remove commented out logarithmic model

%XXX logarithmic Alternative XXX
%In this case we define the residual of the data from the model in
%terms of the logarithmic differences.  This logarithmic formulation
%requires that $d$ be everywhere positive, and distorts the
%uncertainties, especially at low S/N ratio.  The advantages of
%defining the residual in this way are that the model remains linear
%(and therefore fast) and the calibration vector is forced to be
%positive everywhere.  Additionally, at high signal to noise the
%distortion of the uncertainties will be minimal.

%The calibration-vector and Gaussian-Process modified log-likelihood is
%\begin{eqnarray}\label{eq:spectroscopicLF}
%\ln p(d\given\theta,\alpha) &=&
%                                -\frac{1}{2}\,\left[\transpose{\Delta}\,C^{-1}\,\Delta
%                                + \ln([2\pi]^N\,\det{C}) \right]
%\\
%\Delta &\equiv& \ln d - \ln \mu(\theta) - \ln f(\alpha) 
%\\
%C_{nn'} &\equiv& [\hat{\sigma}_n^2 + s^2]\,\delta_{nn'} +
%K_\alpha(\lambda_n - \lambda_{n'})
%\\
%\hat{\sigma_n} & = &\sigma_n/d
%\quad ,
%\end{eqnarray}
%where $\hat{\sigma}_n$ are the fractional uncertainties of the data.
%The residual column vector is defined in terms of the logarithmic
%difference between the data and the mean model $\mu$ since we are
%taking the calibration vector to be multiplicative with respect to the
%mean model $\mu$. In this formulation the the mean model $\mu$ will be
%effectively multiplied by $e ^{f(\alpha)}$

@@

Nebular emission lines (which may arise from HII regions around the
clusters or from diffuse ionized gas) and interstellar absorption
lines are modeled as a sum of $\delta$-functions of unknown amplitude
$a_\ell$, and with known central wavelengths $\lambda_\ell$, broadened
by the gas velocity profile, $\sigma_{gas}$.  For emission lines the
amplitudes are constrained to be positive, while for interstellar
absorption (e.g. NaD and CaK) the amplitudes are constrained to be
negative. This framework can be easily extended to include more
complex models for the nebular emission, such as allowing line
dependent widths and velocities, and using Voight profiles for the
line shapes.

@@

Our strategy is easily extensible to more complicated models, which
include for example night sky-line emission in the spectroscopy
\citep[e.g.,][]{gullikson14} or residuals from an initial sky-line
subtraction and uncertainties in wavelength calibration
\citep[e.g.,][]{walker15}. Furthermore, more complex physical models
may be considered for the mean object model, for example including SFH
parameters so as to model galaxies. {\color{blue} Discuss background
modeling}

@@

Limitations.  The strategy we have advocated has several limitations.
First, it requires a generative model for the spectrum of the object
of interest, and is thus ill-suited to discovery projects.  Second,
care must be taken to avoid absorbing interesting model deficiencies
into the calibration model. For example, in the model we have
described, it is possible that broad shallow features (for example due
to molecular bands or absorption line complexes) will be absorbed into
the Gaussian process if not properly included in the mean
model. Third, we have made the assumption that the spectroscopy and
the photometry are sampling the same populations.  In practice,
differences between spectroscopic and photometric apertures often mean
that the photometry and the spectroscopy are sampling slightly
different physical regions.  The correct response to this situation is
to explicitly model the differences, incorporating prior information
about the spatial variation of physical properties.  Finally, this
method is computationally intensive and expensive, since we are
constantly inverting largish matrices.

>>>>

@@

%Nebular emission lines (which may arise from HII regions around the
%clusters or from diffuse ionized gas) and interstellar absorption
%lines are modeled as a sum of $\delta$-functions of unknown amplitude
%$a_\ell$, and with known central wavelengths $\lambda_\ell$, broadened
%by the gas velocity profile, $\sigma_{gas}$.  For emission lines the
%amplitudes are constrained to be positive, while for interstellar
%absorption (e.g. NaD and CaK) the amplitudes are constrained to be
%negative. This framework can be easily extended to include more
%complex models for the nebular emission, such as allowing line
%dependent widths and velocities, and using Voight profiles for the
%line shapes.

@@

Our strategy is easily extensible to more complicated models, which
include for example nebular or night sky-line emission in the
spectroscopy \citep[e.g.,][]{gullikson14} or residuals from an initial
sky-line subtraction and uncertainties in wavelength calibration
\citep[e.g.,][]{walker15}. Furthermore, more complex physical models
may be considered for the mean object model, for example including SFH
parameters so as to model galaxies. {\color{blue} Discuss background
modeling}

@@

Limitations.  The strategy we have advocated has several limitations.
First, it requires a generative model for the spectrum of the object
of interest, and is thus ill-suited to discovery projects.  Second,
care must be taken to avoid absorbing interesting model deficiencies
into the calibration model. For example, in the model we have
described, it is possible that broad shallow features (for example due
to molecular bands or absorption line complexes) will be absorbed into
the Gaussian Process if not properly included in the mean model. The
Gaussian process will also absorb incorrectly modeled attenuation
curve shapes. Third, we have made the assumption that the spectroscopy
and the photometry are sampling the same populations.  In practice,
differences between spectroscopic and photometric apertures often mean
that the photometry and the spectroscopy are sampling slightly
different physical regions.  The correct response to this situation is
to explicitly model the differences, incorporating prior information
about the spatial variation of physical properties.  Finally, this
method is computationally intensive and expensive, since we are
constantly inverting largish matrices.
